\documentclass{resume}

\usepackage{amssymb}
\usepackage{hyperref}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter 
% 		will be reset to account for marginparsep]
% 
\setlength{\oddsidemargin}{1.1in}
\setlength{\marginparwidth}{1.1in}
% 
% calculate other dimensions [textwidth and evensidemargin] 
% in function of oddsidemargin and marginparwidth: 
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-0.5in}
%
%
\renewcommand{\labelcitem}{$\rhd$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }
\author{~~~~~~Edouard Swiac}
% ------ Address --------------------------------------------------------

\address{
    124 Dolores Street\\
    94103 San Francisco, CA\\
    }{
	Mobile +1 (415) 373-2433\\
	http://edouardswiac.net\\
    edouard.swiac@gmail.com
}

\begin{document}
\maketitle

% ------- Education ---------------------------------------------------

\begin{category}{Education}
\citem{\href{http://www.supinfo.com/}{SUPINFO International University}}, San Francisco, CA.\\
M.Sc in Computer Science, expected November 2011.\\
Thesis title: \emph{Distributed VoIP systems}
\citem{\href{http://www.dominican.edu/}{Dominican University of California}}, San Rafael, CA.\\
Certificate in Management and Marketing of IT, expected November 2011.
\citem{\href{http://www.supinfo.com/}{SUPINFO International University}}, Paris, France.\\
B.Sc in Computer Science, November 2010.\\
Focus on software engineering, web applications and distributed systems.
\end{category}

% --------- Research ----------------------------------------------------

\begin{category}{Skills}
\citemnobullet 
Erlang, Python, PHP, Java, HTTP/REST, SQL/NoSQL, git, Linux/UNIX\\
Exposure to Agile development, Distributed systems, Cloud computing
\end{category}

\begin{category}{Work Experience}
\citem{Erlang software developer},  \href{http://www.2600hz.com/}{2600Hz}, San Francisco CA (April 2011 - \emph{October 2011})\\
Development of Erlang modules for \emph{Whistle}, an open-source distributed VoIP platform built on FreeSWITCH.\\
Added RESTful APIs for Erlang modules like voicemails or hotdesking for language agnostic 
management of the platform.\\
Writing of Unit tests and wiki documentation.

\citem{Java software developer}, \href{http://www.agendize.com/}{Agendize}, Troyes France (November 2010 - March 2011)\\
Implementation of \href{http://www.ietf.org/rfc/rfc4791.txt}{CalDAV (RFC 4791)} for the company's calendar software.

\citem{Java software developer}, \href{http://www.sellermania.co.uk/}{Sellermania}, Paris France (July 2010 - October 2010)\\
Developped a Java heuristic that improves the repricing frequency and accuracy of millions of 
products sold on Amazon France, UK and Germany websites by 104\%, 
increasing daily repricing capacity from 20 million to 208 million items.

\citem{Javascript SDET associate}, \href{http://www.wakanda.org/}{4D/Wakanda}, Paris France (February 2010 - June 2010)\\
Wrote tests cases and use cases for the javascript framework shipped with the RIA platform.

\citem{PHP software developer}, \href{http://www.usine23.com/}{Usine23}, Troyes France (July 2008 - January 2010)\\
-Developed a software solution which streamlines the company’s sales on main e-commerce channels. Written in PHP, it implements Amazon Seller Central SOAP API and eBay SOAP API to sell products and import orders. Solved the batch processing of 7000 products, stock synchronization between three marketplaces, external orders import and integration. This software increased sales by 40\%.\\
-Trained the technical team on different PHP and software engineering subjects (design patterns, PHP SPL, web architectures).\\
-Designed and developed a RESTful API in PHP to open the company’s online retail website, www.goostor.com, to external sellers.
\end{category}

\begin{category}{Community} 
\citemnobullet Creator of the \href{http://javalabsf.net/}{SUPINFO student Java SF usergroup}
Led the student usergroup, gave talks on Continuous Integration, Unit Testing
\citemnobullet Creator of supalumni.net, a web application for SUPINFO alumni, as my participation to the school's best student project challenge. 
Used Django, nginx, PostgreSQL.
\end{category}

\end{document}